### 2021-09-02 manuscript/methodology.tex

Let $\mathbf{d}^{o}$ be the $N \times 1$ observed data vector, whose $i$th element 
is the total-field anomaly $d^{o}_{i}$ produced by arbitrarily magnetized sources
at the position $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $, 
of a right-handed Cartesian coordinate system with $x$-, $y$- and $z$-axis 
pointing to north, east and down, respectively.
We consider that the total-field anomaly data $d^{o}_{i}$ represent the discrete
values of a harmonic function. Besides, we consider that the main geomagnetic field 
direction at the study area can be defined by the unit vector
\begin{equation}
\hat{\mathbf{F}} = \begin{bmatrix}
F_x \\
F_y \\
F_z
\end{bmatrix} =
\begin{bmatrix}
\cos(I_{0}) \, \cos(D_{0}) \\
\cos(I_{0}) \, \sin(D_{0}) \\
\sin(I_{0})
\end{bmatrix} \: ,
\label{eq:unit_vector_F}
\end{equation}
with constant inclination $I_{0}$ and declination $D_{0}$.
In this case, $d^{o}_{i}$ can be approximated by the predicted total-field anomaly
\begin{equation}
\Delta T_{i} = \sum_{j=1}^{M} \, p_{j} a_{ij} \: ,
\label{eq:integral-sum_mag}
\end{equation}
which describes the magnetic induction exerted, at the observation point $(x_{i}, y_{i}, z_{i})$,
by a discrete layer of $M$ dipoles (equivalent sources) defined on the horizontal plane $z = z_{c}$, 
where $p_{j}$ is the magnetic moment intensity (in A~m~$^{2}$)~of the $j$th dipole, 
that has unit volume and is located at the point $(x_{j}, y_{j}, z_{c})$. In equation
\ref{eq:integral-sum_mag}, $a_{ij}$ is the harmonic function
\begin{equation}
a_{ij}
= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{h}} \: ,
\label{eq:aij_mag}
\end{equation}
the unit vector
\begin{equation}
\hat{\mathbf{h}} = \begin{bmatrix}
h_x \\
h_y \\
h_z
\end{bmatrix} =
\begin{bmatrix}
\cos(I) \, \cos(D) \\
\cos(I) \, \sin(D) \\
\sin(I)
\end{bmatrix} \: ,
\label{eq:h_hat}
\end{equation}
defines the magnetization direction of all dipoles, with constant inclination $I$ and declination $D$,
$\mu_{0} = 4\pi \, 10^{-7}$ H/m is the magnetic constant, $c_{m} = 10^{9}$ is a factor that transforms
the magnetic induction from Tesla (T) to nanotesla (nT) and $\mathbf{H}_{ij}$ is a $3 \times 3$ matrix 
\begin{equation}
\mathbf{H}_{ij} = \begin{bmatrix}
\partial_{xx} \frac{1}{r_{ij}} & 
\partial_{xy} \frac{1}{r_{ij}} & 
\partial_{xz} \frac{1}{r_{ij}} \\
\partial_{xy} \frac{1}{r_{ij}} & 
\partial_{yy} \frac{1}{r_{ij}} & 
\partial_{yz} \frac{1}{r_{ij}} \\
\partial_{xz} \frac{1}{r_{ij}} & 
\partial_{yz} \frac{1}{r_{ij}} & 
\partial_{zz} \frac{1}{r_{ij}}
\end{bmatrix} \: ,
\label{eq:Hij}
\end{equation}
where $\partial_{\alpha\beta} \frac{1}{r_{ij}}$, $\alpha = x, y, z$, $\beta = x, y, z$, 
represent the second derivatives of the inverse distance function
\begin{equation}
\frac{1}{r_{ij}} = 
\frac{1}{\sqrt{\left(x_{i} - x_{j} \right)^{2} + 
\left(y_{i} - y_{j} \right)^{2} + \left(z_{i} - z_{c} \right)^{2}}}
\label{eq:1_rij}
\end{equation}
with respect to the coordinates of the observation point $(x_{i}, y_{i}, z_{i})$.

@@

@@

	2 - $\mathbf{c}_{(it)} = \mathbf{r}_{(it)} - \beta_{(it)} \, \mathbf{c}_{(it - 1)}$

@@

%======================================================================================
\subsection{Non-symmetric Block-Toeplitz Toeplitz-Block structure of matrix $\mathbf{A}$}
%======================================================================================

Let us consider that the observed total-field anomaly is located on an $N_x \times N_y$ regular grid of points spaced by $\Delta_x$ and $\Delta_y$ along the $x$- and $y$-directions, respectively.
The notation used in this work will be the same as the one presented in \cite{takahashi2020convolutional}, where the authors described the structure of the symmetric Block-Toeplitz Toeplitz-Block matrix of the gravimetric equivalent layer. Here, we also establish a relation between the pair of \emph{matrix coordinates} $(x_i, y_i)$, $i = 1, ..., N$ or $(x_j, y_j)$, $j = 1, ..., M = N $ and a pair of \emph{grid coordinates} $(x_k, y_l)$ given as:
\begin{equation}
x_{i} \equiv x_{k} = x_{1} + \left[ k(i) - 1 \right] \, \Delta x \: , 
\label{eq:xi}
\end{equation}
and
\begin{equation}
y_{i} \equiv y_{l} = y_{1} + \left[ l(i) - 1 \right] \, \Delta y \: .
\label{eq:yi}
\end{equation}
In a $x$-\textit{oriented grid} the indices $i$ (or $j$) relate as integer functions of $k$ and $l$ by:
\begin{equation}
i(k, l) = (l - 1) \, N_{x} + k \: ,
\label{eq:i-x-oriented}
\end{equation}
\begin{equation}
l(i) = \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil
\label{eq:l-x-oriented}
\end{equation}
and
\begin{equation}
k(i)  = i - \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil N_{x} + N_{x} \: .
\label{eq:k-x-oriented}
\end{equation}
For  $y$-\textit{oriented grid} they are given by:
\begin{equation}
i(k, l) = (k - 1) \, N_{y} + l \: ,
\label{eq:i-y-oriented}
\end{equation}
\begin{equation}
k(i) = \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil
\label{eq:k-y-oriented}
\end{equation}
and
\begin{equation}
l(i) = i - \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil N_{y} + N_{y} \: ,
\label{eq:l-y-oriented}
\end{equation}
where in equations \ref{eq:l-x-oriented} to \ref{eq:l-y-oriented}, $\lceil .\rceil$ is the celing function.
Figure \ref{fig:methodology} shows an example of a grid $N_{x} \times N_{y}$, where $N_{x} = 4$ and $N_{y} = 3$ demonstrating the relation between the \emph{matrix coordinates} with $k(i)$ and $l(i)$ depending on the orientation of the grid.

The $N \times M$ sensitivity matrix  $\mathbf{A}$ (equation \ref{eq:aij_mag}) can be represented as a grid of $Q \times Q$ blocks $\mathbf{A}^q$, $q = -Q+1,...,0,..., Q-1$. Each block  $\mathbf{A}^q$ has $P \times P$ elements $a^{q}_p$ where $p = -P+1^,...,0,...,P-1$

>>>>

Let $\mathbf{d}^{o}$ be the $N \times 1$ observed data vector, whose $i$th element 
is the total-field anomaly $d^{o}_{i}$ produced by arbitrarily magnetized sources
at the position $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $, 
of a right-handed Cartesian coordinate system with $x$-, $y$- and $z$-axis 
pointing to north, east and down, respectively.
We consider that the total-field anomaly data $d^{o}_{i}$ represent the discrete
values of a harmonic function. Besides, we consider that the main geomagnetic field 
direction at the study area can be defined by the unit vector
\begin{equation}
\hat{\mathbf{F}} = \begin{bmatrix}
F_x \\
F_y \\
F_z
\end{bmatrix} =
\begin{bmatrix}
\cos(I_{0}) \, \cos(D_{0}) \\
\cos(I_{0}) \, \sin(D_{0}) \\
\sin(I_{0})
\end{bmatrix} \: ,
\label{eq:unit_vector_F}
\end{equation}
with constant inclination $I_{0}$ and declination $D_{0}$.
In this case, $d^{o}_{i}$ can be approximated by the predicted total-field anomaly
\begin{equation}
\Delta T_{i} = \sum_{j=1}^{M} \, p_{j} a_{ij} \: ,
\label{eq:integral-sum_mag}
\end{equation}
which describes the magnetic induction exerted, at the observation point $(x_{i}, y_{i}, z_{i})$,
by a discrete layer of $M$ dipoles (equivalent sources) defined on the horizontal plane $z = z_{c}$, 
where $p_{j}$ is the magnetic moment intensity (in A~m~$^{2}$)~of the $j$th dipole, 
that has unit volume and is located at the point $(x_{j}, y_{j}, z_{c})$. In equation
\ref{eq:integral-sum_mag}, $a_{ij}$ is the harmonic function
\begin{equation}
a_{ij}
= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{u}} \: ,
\label{eq:aij_mag}
\end{equation}
the unit vector
\begin{equation}
\hat{\mathbf{u}} = \begin{bmatrix}
u_x \\
u_y \\
u_z
\end{bmatrix} =
\begin{bmatrix}
\cos(I) \, \cos(D) \\
\cos(I) \, \sin(D) \\
\sin(I)
\end{bmatrix} \: ,
\label{eq:u_hat}
\end{equation}
defines the magnetization direction of all dipoles, with constant inclination $I$ and declination $D$,
$\mu_{0} = 4\pi \, 10^{-7}$ H/m is the magnetic constant, $c_{m} = 10^{9}$ is a factor that transforms
the magnetic induction from Tesla (T) to nanotesla (nT) and $\mathbf{H}_{ij}$ is a $3 \times 3$ matrix 
\begin{equation}
\mathbf{H}_{ij} = \begin{bmatrix}
h^{xx}_{ij} & h^{xy}_{ij} & h^{xz}_{ij} \\
h^{xy}_{ij} & h^{yy}_{ij} & h^{yz}_{ij} \\
h^{xz}_{ij} & h^{yz}_{ij} & h^{zz}_{ij}
\end{bmatrix} \: ,
\label{eq:Hij}
\end{equation}
where 
\begin{equation}
h^{\alpha\beta}_{ij} = 
\begin{cases}
\frac{3 \left( \alpha_{i} - \alpha_{j} \right)^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: , \quad \alpha = \beta \\
\frac{3 \left( \alpha_{i} - \alpha_{j} \right) \left( \beta_{i} - \beta_{j} \right)}{r_{ij}^{5}} \: , \quad \alpha \ne \beta
\end{cases} \: , \quad \alpha, \beta = x, y, z \: ,
\label{eq:hij_alpha_beta}
\end{equation}
are the second derivatives of the inverse distance function
\begin{equation}
\frac{1}{r_{ij}} = 
\frac{1}{\sqrt{\left(x_{i} - x_{j} \right)^{2} + 
\left(y_{i} - y_{j} \right)^{2} + \left(z_{i} - z_{c} \right)^{2}}}
\label{eq:1_rij}
\end{equation}
with respect to the coordinates of the observation point $(x_{i}, y_{i}, z_{i})$.

@@

The computational cost required for estimating the classical solution can be very high
when dealing with large datasets. In the following subsections, we will show how to 
explore the structure of the sensitivity matrix $\mathbf{A}$ and use this to
efficiently solve the least-squares normal equations (equation \ref{eq:normal-equations}).

%=====================================================================================================
\subsection{Matrix $\mathbf{A}$ in terms of matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$}
%=====================================================================================================

To access the structure of the sensitivity matrix $\mathbf{A}$ 
(equation \ref{eq:predicted-data-vector_mag}), let us first rewrite its elements 
$a_{ij}$ (equation \ref{eq:aij_mag}) in the following way:
\begin{equation}
\begin{split}
a_{ij} = a^{xx}_{ij} + a^{xy}_{ij} + a^{xz}_{ij} + a^{yy}_{ij} + a^{yz}_{ij} + a^{zz}_{ij} \: ,
\end{split}
\label{eq:aij_mag_expand}
\end{equation}
where
\begin{equation}
a^{\alpha\beta}_{ij} = c_{m} \, \frac{\mu_{0}}{4\pi} 
\left( F_{\alpha} h_{\beta} + F_{\beta} h_{\alpha} \right) h^{\alpha\beta}_{ij}
\: , \quad \alpha, \beta = x, y, z \: ,
\label{eq:aij_alpha_beta}
\end{equation}
are defined by the elements of $\hat{\mathbf{F}}$ 
(equation \ref{eq:unit_vector_F}), $\hat{\mathbf{u}}$ (equation \ref{eq:u_hat}) and 
$\mathbf{H}_{ij}$ (equations \ref{eq:Hij} and \ref{eq:hij_alpha_beta}).
Then, we can rewrite the sensitivity matrix $\mathbf{A}$ 
(equation \ref{eq:predicted-data-vector_mag}) according to:
\begin{equation}
\mathbf{A} = \mathbf{A_{xx}} + \mathbf{A_{xy}} + \mathbf{A_{xz}} + 
\mathbf{A_{yy}} + \mathbf{A_{yz}} + \mathbf{A_{zz}} \: ,
\label{eq:A_expand}
\end{equation}
where $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ are $N \times M$ matrices with elements 
$ij$ defined by $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}).

Now we can define the structure of $\mathbf{A}$ in terms of its components 
$\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}). To do this, 
let us consider that the observed total-field anomaly is located on an $N_{x} \times N_{y}$ 
regular grid of points spaced by $\Delta_{x}$ and $\Delta_{y}$ along the $x$- and $y$-directions,
respectively, on a constant vertical coordinate $z_{0}$. We also consider that the equivalent layer
is formed by one dipole right below each observation point, at the constant coordinate $z_{c}$.
In this case, the number of equivalent sources $M$ is equal to the number of data $N$ and, 
consequently, matrices $\mathbf{A}$ and $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ become 
square ($N \times N$). 
Besides, the horizontal coordinates $x_{i}$ and $y_{i}$ of the observation points 
can be defined by
\begin{equation}
x_{i} = x_{1} + \left[ k(i) - 1 \right] \, \Delta_{x}
\label{eq:xi}
\end{equation}
and
\begin{equation}
y_{i} = y_{1} + \left[ l(i) - 1 \right] \, \Delta_{y} \: ,
\label{eq:yi}
\end{equation}
where $x_{1}$ and $y_{1}$ are the lower limits for $x_{i}$ and $y_{i}$, respectively,
and $k(i)$ and $l(i)$ are integer functions defined according to the orientation
of the data grid (For details, please refer to \citet{takahashi2020convolutional}). 
For $x$-\textit{oriented grids}, the integer functions are given by
\begin{equation}
k(i)  = i - \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil N_{x} + N_{x}
\label{eq:k-x-oriented}
\end{equation}
and
\begin{equation}
l(i) = \Bigg\lceil \frac{i}{N_{x}} \Bigg\rceil \: .
\label{eq:l-x-oriented}
\end{equation}
For $y$-\textit{oriented grids}, the integer functions are given by
\begin{equation}
k(i) = \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil
\label{eq:k-y-oriented}
\end{equation}
and
\begin{equation}
l(i) = i - \Bigg\lceil \frac{i}{N_{y}} \Bigg\rceil N_{y} + N_{y} \: .
\label{eq:l-y-oriented}
\end{equation}
In equations \ref{eq:k-x-oriented}--\ref{eq:l-y-oriented}, $\lceil \cdot \rceil$ denotes the ceiling 
function \citep[e.g.,][ p. 67-68]{graham-etal1994}.
Equations \ref{eq:xi}--\ref{eq:l-y-oriented} can also be used to define the coordinates 
$x_{j}$ and $y_{j}$ of the equivalent sources, but with index $j$ instead of $i$.

By using equations \ref{eq:xi}--\ref{eq:l-y-oriented} to define the coordinates $x_{i}$ and 
$y_{i}$ of the observation points and $x_{j}$ and $y_{j}$ of the equivalent sources, we can
rewrite the elements $h^{\alpha\beta}_{ij}$ (equation \ref{eq:hij_alpha_beta}) of matrix 
$\mathbf{H}_{ij}$ (equation \ref{eq:Hij}) as follows:
\begin{equation}
h^{xx}_{ij} = 
\frac{3 \left( \Delta k_{ij} \, \Delta_{x} \right)^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: ,
\label{eq:hxx_regular}
\end{equation}
\begin{equation}
h^{yy}_{ij} = 
\frac{3 \left( \Delta l_{ij} \, \Delta_{y} \right)^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: ,
\label{eq:hyy_regular}
\end{equation}
\begin{equation}
h^{zz}_{ij} = 
\frac{3 \Delta_{z}^{2}}{r_{ij}^{5}} - \frac{1}{r_{ij}^{3}} \: ,
\label{eq:hzz_regular}
\end{equation}
\begin{equation}
h^{xy}_{ij} = 
\frac{3 \left( \Delta k_{ij} \, \Delta_{x} \right)\left( \Delta l_{ij} \, \Delta_{y} \right)}{r_{ij}^{5}} \: ,
\label{eq:hxy_regular}
\end{equation}
\begin{equation}
h^{xz}_{ij} = 
\frac{3 \left( \Delta k_{ij} \, \Delta_{x} \right) \Delta_{z}}{r_{ij}^{5}}
\label{eq:hxz_regular}
\end{equation}
and
\begin{equation}
h^{yz}_{ij} = 
\frac{3 \left( \Delta l_{ij} \, \Delta_{y} \right) \Delta_{z}}{r_{ij}^{5}}
\label{eq:hyz_regular}
\end{equation}
where $\Delta_{z} = z_{c} - z_{0}$, $\Delta k_{ij} = k(i) - k(j)$ (equations \ref{eq:k-x-oriented} or \ref{eq:k-y-oriented}), $\Delta l_{ij} = l(i) - l(j)$ (equations \ref{eq:l-x-oriented} or \ref{eq:l-y-oriented}) and
\begin{equation}
\frac{1}{r_{ij}} = 
\frac{1}{\sqrt{\left( \Delta k_{ij} \, \Delta_{x} \right)^{2} + \left( \Delta l_{ij} \, \Delta_{y} \right)^{2} + \Delta_{z}^{2}}} \: .
\label{eq:1_rij_regular}
\end{equation}

%==================================================================================
\subsection{Matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ in terms of block indices $q$ and $p$}
%==================================================================================

By using equations \ref{eq:hxx_regular}--\ref{eq:1_rij_regular} to compute 
$a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}), we obtain well-structured 
block matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}).
All of them are formed by a grid of $Q \times Q$, where each block has $P \times P$ 
elements. The blocks disposed along the same block diagonal are equal to each other.
In each block, the elements disposed on the same diagonal are also equal to each other.
Such matrices are called Block-Toeplitz Toeplitz-Block (BTTB) and they can be conveniently
represented by using \textit{block indices} $q$ and $p$ \citep{takahashi2020convolutional}.
Here, each block is represented by $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$, 
$q = -Q+1,...,0,..., Q-1$, and their elements by $a^{\alpha\beta}_{qp}$, 
$p = -P+1,...,0,...,P-1$. 
Positive (negative) indices $q$ represent blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ 
located below (above) the main block diagonal of $\mathbf{A}_{\boldsymbol{\alpha\beta}}$.
Similarly, positive (negative) indices $p$ represent elements $a^{\alpha\beta}_{qp}$ 
located below (above) the main diagonal of $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$.
According to this notation, $q$ defines the block $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$
and $p$ the diagonal where the element $a^{\alpha\beta}_{qp}$ is located within this block, so that
matrices $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ 
can be written, in a general form, as a grid of $Q \times Q$ blocks
\begin{equation}
\mathbf{A}_{\boldsymbol{\alpha\beta}} = \begin{bmatrix}
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{0}   & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-1} & \cdots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-Q+1} \\
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{1}   & \ddots          & \ddots          & \vdots           \\ 
\vdots           & \ddots          & \ddots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{-1}   \\
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{Q-1} & \cdots          & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{1}  & \mathbf{A}_{\boldsymbol{\alpha\beta}}^{0}
\end{bmatrix}_{N \times N} \: ,
\label{eq:BTTB_A_alpha_beta}
\end{equation}
with blocks $\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ given by
\begin{equation}
\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q} = \begin{bmatrix}
a^{\alpha\beta}_{q0}   & a^{\alpha\beta}_{q(-1)} & \cdots  & a^{\alpha\beta}_{q(-P+1)} \\
a^{\alpha\beta}_{q1}   & \ddots     & \ddots  & \vdots       \\ 
\vdots      & \ddots     & \ddots  & a^{\alpha\beta}_{q(-1)}   \\
a^{\alpha\beta}_{q(P-1)} & \cdots     & a^{\alpha\beta}_{q1}  & a^{\alpha\beta}_{q0}
\end{bmatrix}_{P \times P} \: .
\label{eq:Aq_block}
\end{equation}
It is important to stress that $a^{\alpha\beta}_{qp}$ (equation \ref{eq:Aq_block}), 
$q = -Q+1,...,0,..., Q-1$, $p = -P+1,...,0,...,P-1$, represents an alternative notation
to describe the elements $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta}) of the matrix
components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$ (equation \ref{eq:A_expand}) in terms of 
the block indices $q$ and $p$. This notation allows us to verify that: (i) different combinations
of indices $i$ and $j$ result in elements $a^{\alpha\beta}_{ij}$ having the same numerical 
value; (ii) these elements are located on the diagonal $p$ of a block 
$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ (equation \ref{eq:Aq_block}); (iii) the same block 
$\mathbf{A}_{\boldsymbol{\alpha\beta}}^{q}$ appears along the block diagonal $q$ of the 
matrix component $\mathbf{A}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:BTTB_A_alpha_beta}).

The relationship between a given element $a^{\alpha\beta}_{ij}$ (equation \ref{eq:aij_alpha_beta})
and an element $a^{\alpha\beta}_{qp}$ is defined by the block indices $q$ and $p$ 
and the integer functions $\Delta k_{ij}$ and $\Delta l_{ij}$ 
(equations \ref{eq:hxx_regular}--\ref{eq:1_rij_regular}).
For $x$-\textit{oriented grids}, $Q = N_{y}$, $P = N_{x}$ and the block indices
$q$ and $p$ are given by:
\begin{equation}
q(i, j) = \Delta l_{ij} = l(i) - l(j)
\label{eq:q-x-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \Delta k_{ij} =  k(i) - k(j) \: ,
\label{eq:p-x-oriented}
\end{equation}
where $k(i)$ and $k(j)$ are given by equation \ref{eq:k-x-oriented} and 
$l(i)$ and $l(j)$ by equation \ref{eq:l-x-oriented}.
For $y$-\textit{oriented grids}, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are given by:
\begin{equation}
q(i, j) = \Delta k_{ij} = k(i) - k(j) 
\label{eq:q-y-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \Delta l_{ij} = l(i) - l(j) \: ,
\label{eq:p-y-oriented}
\end{equation}
where $k(i)$ and $k(j)$ are given by equation \ref{eq:k-y-oriented} and 
$l(i)$ and $l(j)$ by equation \ref{eq:l-y-oriented}.
Equations \ref{eq:q-x-oriented}--\ref{eq:p-y-oriented} differ from those presented by
\citet{takahashi2020convolutional} in the absence of the module.

% in review ==========>

%==================================================================================
\subsection{Structure of matrix components $\mathbf{A_{\boldsymbol{\alpha\beta}}}$}
%==================================================================================

In general, matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is a non-symmetric BTTB, i.e., its blocks are non-symmetric ($\mathbf{A}^{-Q+1} \neq \mathbf{A}^{Q-1} $) and its elements also are non-symmetric ($a^{q}_{-1} \neq a^{q}_{1}$). Depending on specific values of the main field direction and the equivalent sources magnetization directions, matrix $\mathbf{A}$ can assume other structures, for example, when $\hat{\mathbf{F}} = [0, 0, 1]$ and $\hat{\mathbf{u}} = [0, 0, 1]$ it becomes symmetric. In this work, we are considering the more commom situation for the matrix $\mathbf{A}$.

%======================================================================================
%\subsection{Structure of matrices components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$}
%======================================================================================

The principal components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ (equations \ref{eq:hxx_mag}, \ref{eq:hyy_mag} and \ref{eq:hzz_mag}, respectively) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are symmetric-Block-Toeplitz symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ are Toeplitz and symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices. 
For example, $\mathbf{H_{xx}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = 0, \dots, Q - 1$:
\begin{equation}
\mathbf{H_{xx}} = \begin{bmatrix}
\mathbf{H}^{0}_\mathbf{xx}  & \mathbf{H}^{1}_\mathbf{xx} & \cdots         & \mathbf{H}^{Q-1}_\mathbf{xx} \\
\mathbf{H}^{1}_\mathbf{xx}  & \mathbf{H}^{0}_\mathbf{xx} & \ddots         & \vdots           \\ 
\vdots           & \ddots         & \ddots         & \mathbf{H}^{1}_\mathbf{xx}   \\
\mathbf{H}^{Q-1}_\mathbf{xx} & \cdots         & \mathbf{H}^{1}_\mathbf{xx} & \mathbf{H}^{0}_\mathbf{xx}                
\end{bmatrix}_{N \times N} \: .
\label{eq:BTTB_Hxx}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = 0, \dots, P - 1$:
\begin{equation}
\mathbf{H}^{q}_\mathbf{xx} = \{h^{q}_p\} = \begin{bmatrix}
h^{q}_{0}   & h^{q}_{1} & \cdots    & h^{q}_{P-1} \\
h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
\vdots      & \ddots    & \ddots    & h^{q}_{1}   \\
h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
\end{bmatrix}_{P \times P} \: .
\label{eq:Hxx_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_{x}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
q(i, j) = \; \mid l(i) - l(j) \mid
\label{eq:Hxx-q-x-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; \mid k(i) - k(j) \mid \quad ,
\label{eq:Hxx-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
q(i, j) = \; \mid k(i) - k(j) \mid 
\label{eq:Hxx-q-y-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; \mid l(i) - l(j) \mid \quad ,
\label{eq:Hxx-p-y-oriented}
\end{equation}
This struture can also describe matrices $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ in the same manner and they are identical to the structure of the gravity sensitivity matrix from \cite{takahashi2020convolutional}.

%======================================================================================
%\subsection{Structure of the components matrices $\mathbf{H_{xy}}$}
%======================================================================================

%======================================================================================
%\subsection{Structure of the components matrices $\mathbf{H_{xz}}$}
%======================================================================================

%======================================================================================
%\subsection{Structure of the components matrices $\mathbf{H_{yz}}$}
%======================================================================================

The component $\mathbf{H_{yz}}$ (equation \ref{eq:hyz_mag}) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{yz}}$ is Toeplitz and symmetric by its blocks and each of the blocks are skew symmetric Toeplitz matrices.
Thus, matrix $\mathbf{H_{yz}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{yz}$, $q = 0, \dots, Q - 1$:
\begin{equation}
\mathbf{H_{yz}} = \begin{bmatrix}
\mathbf{H}^{0}_\mathbf{yz}  & \mathbf{H}^{1}_\mathbf{yz} & \cdots         & \mathbf{H}^{Q-1}_\mathbf{yz} \\
\mathbf{H}^{1}_\mathbf{yz}  & \mathbf{H}^{0}_\mathbf{yz} & \ddots         & \vdots           \\ 
\vdots           & \ddots         & \ddots         & \mathbf{H}^{1}_\mathbf{yz}   \\
\mathbf{H}^{Q-1}_\mathbf{yz} & \cdots         & \mathbf{H}^{1}_\mathbf{yz} & \mathbf{H}^{0}_\mathbf{yz}                
\end{bmatrix}_{N \times N} \: .
\label{eq:BTTB_Hyz}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = -P + 1, \dots, 0, \dots, P - 1$:
\begin{equation}
\mathbf{H}^{q}_\mathbf{yz} =  \{h^{q}_p\} = \begin{bmatrix}
h^{q}_{0}   & h^{q}_{-1} & \cdots    & h^{q}_{-P+1} \\
h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
\vdots      & \ddots    & \ddots    & h^{q}_{-1}   \\
h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
\end{bmatrix}_{P \times P} \: .
\label{eq:Hyz_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_{x}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
q(i, j) = \; \mid l(i) - l(j) \mid
\label{eq:Hyz-q-x-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; k(i) - k(j) \quad ,
\label{eq:Hyz-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
q(i, j) = \; \mid k(i) - k(j) \mid
\label{eq:Hyz-q-y-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; l(i) - l(j) \quad ,
\label{eq:Hyz-p-y-oriented}
\end{equation}
Being a symmetric matrix by blocks, the values of $\mathbf{H_{yz}}$ from oposing diagonals blocks are equal, but each block have skew symmetric oposing diagonals, i.e., $h^{q}_{-1} = - h^{q}_{1}$.

% <========== in review

@@

	2 - $\mathbf{c}_{(it)} = \mathbf{r}_{(it)} + \beta_{(it)} \, \mathbf{c}_{(it - 1)}$

@@
